Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`

### 2024-09-09 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)

print(dim(srat)[2])
# this would need to be change for CI or whole sample
 s <- RunAzimuth_small(srat, reference ="fetusref", k.weight = 10, mapping.score.k = 80, ksmooth = 80)

# We transfer the annotation to the pre-processed `Seurat`iobject as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.annotation.l1.score", "predicted.annotation.l1", "predicted.annotation.l2.score", "predicted.annotation.l2", "predicted.organ.score", "predicted.organ")

>>>>

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)
s <- Azimuth::RunAzimuth(srat, reference ="fetusref")

# We transfer the annotation to the pre-processed `Seurat` object as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.annotation.l1.score", "predicted.annotation.l1", "predicted.annotation.l2.score", "predicted.annotation.l2", "predicted.organ.score", "predicted.organ")
